--- 
title: "Little Kids, Big Adventures Around Knoxville, Tennessee"
subtitle: "Learning About and Experiencing the Cumberland Plateau, Tennessee Valley, and Great Smoky Mountains"
author: "Katie Rosenberg and Joshua Rosenberg"
date: "Last updated: `r Sys.Date()`"
site: bookdown::bookdown_site
documentclass: book
bibliography: [book.bib, packages.bib]
biblio-style: "apalike"
link-citations: yes
github-repo: "jrosen48/little-kids-big-adventures"
url: "https://littlekidsbigadventures.com"
---

```{r, setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE)
```

```{r, message=FALSE}
library(here)
library(tidyverse)
```

# Introduction {-}

```{block, type='rmddisclaimer'}
This book is a work-in-progress; it is not even at the rough draft stage yet!
```

## Status

This book is not yet even at the rough draft stage; proceed with caution!

## How to use

This book has a slight educational bent---perhaps a result of our backgrounds as educators. This is also because this region is so rich with historical (human and natural) chances to learn about the world. Accordingly, we call out history-related elements of the areas in this book with the following call-out.

```{block, type='rmdhistory', echo = TRUE}
This is for human history-related call-outs.
```

We use the following call-out for scientific tid-bits: those related to living and non-living aspects of the environment that have been studied scientifically, such as the names of plants and animals or the types of rock underfoot.

```{block, type='rmdscience', echo = TRUE}
This is for science-related call-outs.
```

Lastly, a big part of exploring is finding your own tips and tricks and ways to navigate particular places. We highlight some of our tips with this type of call-out.

```{block, type='rmdtip', echo = TRUE}
This is a tip.
```

## Trails

The following trails are included:

```{r, echo = FALSE, message = FALSE}
d <- read_csv("trail-info.csv")

d %>% 
    select(1:3) %>% 
    knitr::kable()
```

## Science 

The following species and topics are discussed:

```{r}
read_csv(here::here("data", "raw", "science.csv")) %>% 
    select(1:2) %>% 
    knitr::kable()
```

## How this book was created

### Overview

This book is initially being written in the "open"; this means that others can and have made suggestions that have improved it. Thank you to those who read and provided feedback on the book. We used the bookdown R package to render the book and GitHub pages to host the book. 

Unless mentioned, we have taken all of the photos used in this book. 

We have also created all of the maps used in this book using publicly-available data. We acknowledge those publicly-available sources next.

### Acknowledgments

Thank you to [Isabella Velásquez](https://ivelasq.rbind.io/) for creating and sharing the R code to create trail maps; this code was essential to being able to create beautiful (we think!) trail maps for this book. 

Thanks to [Tyler Morgan-Wall](https://www.tylermw.com/), whose [tutorial on creating trail maps](https://www.tylermw.com/adding-open-street-map-data-to-rayshader-maps-in-r/) was also instrumental.

Thank you to [Daniel Anderson](https://github.com/datalorax) for the basis for [the theme](https://github.com/datalorax/sds-r/blob/main/style.css) for this book. 

Thank you to Conor Anderson [for the CSS code for the call-out boxes](https://gitlab.com/claut/man_ccia) in this text.

Thank you to Samuel Weisbrod, Aaron Rosenberg, and Kevin Lane for photos included in this book.

Thank you to Amanda Hendricks and Anthony Schmidt for trail and science-related suggestions.

### Credits

[Open Street Map](https://www.openstreetmap.org/copyright) data is used to create the trail maps. 

Map tiles by <a href="http://stamen.com">Stamen Design</a>, under <a href="http://creativecommons.org/licenses/by/3.0">CC BY 3.0</a>. Data by <a href="http://openstreetmap.org">OpenStreetMap</a>, under <a href="http://www.openstreetmap.org/copyright">ODbL</a>.
